---
title: "Precipitation Interpolation"
author: "AJ"
date: "4/18/2022"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)
library(sf) 
library(mapview)
library(lubridate)
library(osmdata)
library(gstat)
library(elevatr)
library(sp)
library(raster)
library(stars)
library(tmap)

knitr::opts_chunk$set(echo = TRUE)
```


# Load in Precip data

```{r}
load('data/DailyP.RData')

head(daily_p)
```


## Get Elevation Data

```{r}
unique_asos <- daily_p %>%
  distinct(lon, lat, station)  %>%
  st_as_sf(., coords = c('lon','lat'), crs = 4326) %>%
  get_elev_point()

st_read('data/unique_asso_elev.gpkg')

```

## Get Monthly P Averages

```{r}
monthly_p <- daily_p %>%
  mutate(month = month(date)) %>%
  group_by(month, station) %>%
  summarize(monthly_p = sum(daily_p)) %>%
  left_join(unique_asos) 

```


## Look at monthly P

```{r}
ggplot(monthly_p, aes(x = elevation, y = monthly_p, color = month)) + 
  scale_color_viridis_c() + 
  geom_point()

```


## Getting Monthly Means of means, mins, maxes in Temp. 

```{r}
monthly_t <- daily_p %>%
  mutate(month = month(date)) %>%
  group_by(month, station) %>%
  dplyr::select(-lon, -lat) %>% 
  summarize(across(where(is.numeric), mean)) %>%
  left_join(unique_asos,.)

```


## Temp vs Elevation

```{r}
ggplot(monthly_t, aes(y = mean_temp, x = elevation, color = month)) + 
  geom_point() + 
  scale_color_viridis_c()
```

# Assignment

## Pick a month (summer months are safer)
```{r} 
July_p <- daily_p %>% 
        st_as_sf(., coords = c('lon','lat'), crs = 4326) %>% 
        mutate(month = month(date)) %>% 
        filter(month == 7) %>% 
        group_by(month, station) %>% 
        summarize(precip = sum(daily_p))

```

### Build IDW precip or elevation for state for that month
```{r}
# Class hint
# get the boundary data of Colorado
CO <- spData::us_states %>% 
      filter(NAME == 'Colorado')

# make a empty grid
CO_2163 <- st_transform(CO, crs=2163)

CO_2163_box <- st_bbox(CO_2163) %>% 
               st_as_stars(dx = 1000) %>% 
               na.omit(.)

# fit the coordinate reference system
July_p <- July_p %>%
          st_transform(., st_crs(CO_2163_box)) %>% 
          na.omit(.)

# interpolation  
interp_July_p <- idw(precip ~ 1, July_p, CO_2163_box) %>% 
                 dplyr::select(1)

```


### Plot this data

```{r}
# using tmap
tm_shape(interp_July_p) +
  tm_raster(palette = 'plasma', style = 'cont',
            title="Total precipitation \n(in) in July 2019") +
tm_legend(legend.outside=TRUE)

# using mapview
mapview(July_p, zcol='precip') + 
mapview(interp_July_p, na.col=NA, 
        col.regions = mapviewGetOption("vector.palette"))

```



### Build IDW with elevation for state for that month including elevation as a predictor

Hint! Use `get_elev_raster`

```{r}
# get elevation raster and make grid
ras <- get_elev_raster(unique_asos, z = 8) %>% 
       raster::crop(., unique_asos)

ras.star <- st_as_stars(ras, dx = 1000) 

names(ras.star) <- "elevation"

# join elevation and precipitation data
unique_asos_July <- st_read('data/unique_asso_elev.gpkg')

July_pe <- daily_p %>% 
           mutate(month = month(date)) %>% 
           group_by(month, station) %>% 
           filter(month == 7) %>%
           summarise(precip = sum(daily_p)) %>%
           left_join(unique_asos_July,.) %>% 
           na.omit(.)

# Interpolation
interp_July_p_elev <- idw(precip ~ elevation, July_pe, ras.star) %>% dplyr::select(1) 

```

### Make a Map of that

```{r}
## You will need to create a Stars raster that has elevation data. 

tm_shape(interp_July_p_elev) + 
  tm_raster(n = 10, palette = "-plasma", midpoint = TRUE,
            title="Total precipitation \n(in) in July 2019") +
tm_legend(legend.outside=TRUE)

```


### Compare both maps to PRISM approach for your month


How close do our simple approaches come to reproducing prism maps? 


https://www.prism.oregonstate.edu/recent/monthly.php

