<<<<<<< HEAD
---
title: "yojoa heat map"
author: "Matthew Ross"
date: "2/22/2019"
output: html_document
---

```{r}
library(tidyverse)
library(sf)
library(mapview)
library(lubridate)
library(osmdata)
library(raster)
library(sp)
library(gstat)

```


# Data read
```{r}
# Read in points
y <- read_csv('data/Yojoaheatmapfile.csv') 
  

ys <- st_as_sf(y,coords=c('longitude','latitude'),crs=4326) 

ys.m <- st_transform(ys,crs=26716) %>%
  mutate(x=st_coordinates(.)[,1],
         y=st_coordinates(.)[,2])



# Get county 
bb <- getbb('Santa Barbara, Honduras')

#Download Lago de Yojoa
lake <- opq(bbox=bb) %>%
add_osm_feature(key = 'natural', value = 'water') %>%
  osmdata_sf() %>%
  .$osm_polygons %>%
  filter(name == 'Lago de Yojoa') %>%
  st_transform(26716)


#Get bboxx info for yojoa
yo_box <- st_bbox(lake)

mapview(ys,zcol='Cu_mg_kg')
mapview(lake)

```

## Make a heatmap
```{r}

lake.sp <- as(lake,'Spatial')
lake.raster <- raster(lake.sp,res=100)
g <- as(lake.raster,'SpatialGrid')


y.sp <- as(ys.m,'Spatial')


metals = c('Cu_mg_kg','Zn_mg_kg','Cd_mg_kg','Pb_mg_kg')


for(i in 1:length(metals)){
  formula = as.formula(paste(metals[i], 1,sep='~'))
  cu_s <- gstat(id=metals[i],formula=formula,data=y.sp)
  z <- interpolate(lake.raster,cu_s) %>% round(.,1)
  z <- mask(z,lake.sp)

  
  cu <- mapview(z,na.col=NA,col.regions=mapviewGetOption('vector.palette')) + 
    mapview(ys.m,zcol=metals[i])
  mapshot(cu,url=paste0(metals[i],'.html'))
}

```

# practice for spatial data
```{r}
library(tidyverse) 
library(sf)
library(mapview)
p1 = st_point(c(7.35, 52.42))
p2 = st_point(c(7.22, 52.18))
p3 = st_point(c(7.44, 52.19))
sfc = st_sfc(list(p1, p2, p3), crs = 'OGC:CRS84')
st_sf(elev = c(33.2, 52.1, 81.2), marker = c("Id01", "Id02", "Id03"),
      geom = sfc)

(file = system.file("gpkg/nc.gpkg", package = "sf"))

nc <- st_read(file)
st_layers(file)

(file = tempfile(fileext = ".gpkg"))
st_write(nc, file, layer = "layer_nc")
class(nc[2:5, 3:7])

nc5 <- nc[1:5,]
nc7 <- nc[1:7,]
(i  <- st_intersects(nc5, nc7))

as.matrix(i)
lengths(i)

methods(class = 'sgbp')

library(tidyverse)
nc %>% as.tibble() %>% select(BIR74) %>% head(3)

orange <- nc %>% dplyr::filter(NAME == "Orange")
wd <- st_is_within_distance(nc, orange, units::set_units(50,km))
o50 <- nc %>% dplyr::filter(lengths(wd) > 0)
nrow(o50)

# example of largest = TRUE:
nc <- st_transform(read_sf(system.file("shape/nc.shp", package="sf")), 2264)
gr = st_sf(
         label = apply(expand.grid(1:10, LETTERS[10:1])[,2:1], 1, paste0, collapse = " "),
         geom = st_make_grid(nc))
gr$col = sf.colors(10, categorical = TRUE, alpha = .3)
# cut, to check, NA's work out:
gr = gr[-(1:30),]
suppressWarnings(nc_j <- st_join(nc, gr, largest = TRUE))

# the two datasets:
opar = par(mfrow = c(2,1), mar = rep(0,4))
plot(st_geometry(nc_j))
plot(st_geometry(gr), add = TRUE, col = gr$col)
text(st_coordinates(st_centroid(st_geometry(gr))), labels = gr$label)

# the joined dataset:
plot(st_geometry(nc_j), border = 'black', col = nc_j$col)
text(st_coordinates(st_centroid(st_geometry(nc_j))), labels = nc_j$label, cex = .5)
plot(st_geometry(gr), border = 'green', add = TRUE)

par(opar)


# stars
tif = system.file("tif/L7_ETMs.tif", package = "stars")
library(stars)
(r <- read_stars(tif))
r
class(r[[1]])

dim(r[[1]])
st_dimensions(r)
st_drivers('raster')

r[1,1:50, 5, 1, drop = TRUE] %>% dim()

slice(r, band,6)

b = st_bbox(r) %>%
    st_as_sfc() %>%
    st_centroid() %>%
    st_buffer(units::set_units(500, m))
r[b]
r[b] %>% st_normalize() %>% st_dimensions()
r[b, crop = FALSE]
(rs = split(r))
merge(rs) 

pts = st_bbox(r) %>% st_as_sfc() %>% st_sample(20)
(e = st_extract(r, pts))


circles = st_sample(st_as_sfc(st_bbox(r)), 3) %>%
    st_buffer(500)
aggregate(r, circles, max)
mapview(circles)

plot(r[,,,1], reset = FALSE)
col = rep("green", 20)
col[c(8, 14, 15, 18, 19)] = "red"
st_as_sf(e) %>% st_coordinates() %>% text(labels = 1:20, col = col)

log(r)
```

```{r}
library(spacetime)
library(stars)
data(air) # this loads several datasets in .GlobalEnv
dim(air)

d = st_dimensions(station = st_as_sfc(stations), time = dates)
(aq = st_as_stars(list(PM10 = air), dimensions = d))

image(aperm(log(aq), 2:1), main = "NA pattern (white) in PM10 station time series")

plot(st_as_sf(st_apply(aq, 1, mean, na.rm = TRUE)), reset = FALSE, pch = 16, ylim = st_bbox(DE)[c(2,4)])
plot(DE, add=TRUE)

(a = aggregate(aq, st_as_sf(DE_NUTS1), mean, na.rm = TRUE))

library(tidyverse)
library(sf)
a %>% filter(time >= "2008-01-01", time < "2008-01-07") %>% 
    plot(key.pos = 2)
supp
suppressPackageStartupMessages(library(xts))
plot(as.xts(a)[,4], main = DE_NUTS1$NAME_1[3])

```
```{r}
(file = system.file("gpkg/nc.gpkg", package="sf"))

read_sf(file) %>% 
  st_geometry() %>% 
  st_as_stars() %>% 
  plot()

library(dplyr)

read_sf(file) %>% 
  mutate(name = as.factor(NAME)) %>% 
  select(SID74, SID79, name) %>% 
  st_rasterize() %>% 
  plot()

read_sf(file) %>% 
    st_cast("MULTILINESTRING") %>% 
    select(CNTY_ID) %>% 
    st_rasterize() %>% 
    plot()

tif = system.file("tif/L7_ETMs.tif", package = "stars")
read_stars(tif) %>%
    st_transform(4326)

read_stars(tif) %>% 
    st_warp(crs = st_crs(4326)) %>% 
    st_dimensions()

r   <- read_stars(tif)
grd <- st_bbox(r) %>% 
       st_as_sfc() %>% 
       st_transform(4326) %>% 
       st_bbox() %>% 
       st_as_stars(nx = dim(r)["x"], ny = dim(r)["y"])

st_warp(r, grd)

```

=======
---
title: "yojoa heat map"
author: "Matthew Ross"
date: "2/22/2019"
output: html_document
---

```{r}
library(tidyverse)
library(sf) # new goodness
library(mapview)
library(lubridate)
library(osmdata)
library(raster) #dead to me
library(sp) # also very dead to me. 
library(gstat)

```


# Data read
```{r}
# Read in points
y <- read_csv('data/Yojoaheatmapfile.csv') 


ys <- st_as_sf(y,coords=c('longitude','latitude'),crs=4326) 

ys.m <- st_transform(ys,crs=26716) %>%
  mutate(x=st_coordinates(.)[,1],
         y=st_coordinates(.)[,2])



# Get state metadata
bb <- getbb('Santa Barbara, Honduras')

#Download Lago de Yojoa
lake <- opq(bbox=bb) %>%
add_osm_feature(key = 'natural', value = 'water') %>%
  osmdata_sf() %>%
  .$osm_polygons %>%
  filter(name == 'Lago de Yojoa') %>%
  st_transform(26716)


#Get bboxx info for yojoa
yo_box <- st_bbox(lake)

mapview(ys,zcol='Cu_mg_kg') + 
  mapview(lake) + 
  mapview(yo_box)
```

## Make a heatmap

```{r}

lake.sp <- as(lake,'Spatial')
lake.raster <- raster(lake.sp,res=100)
g <- as(lake.raster,'SpatialGrid')


y.sp <- as(ys.m,'Spatial')


metals = c('Cu_mg_kg','Zn_mg_kg','Cd_mg_kg','Pb_mg_kg')


for(i in 1:length(metals)){
  
  
  formula = as.formula(paste(metals[i], 1,sep='~'))
  
  cu_s <- gstat(id=metals[i],formula=formula,data=y.sp)
  
  z <- interpolate(lake.raster,cu_s) %>% round(.,1)
  
  z <- mask(z,lake.sp)
  

  
  cu <- mapview(z,na.col=NA,col.regions=mapviewGetOption('vector.palette')) + 
    mapview(ys.m,zcol=metals[i])
  mapshot(cu,url=paste0('out/',metals[i],'.html'))
}

```



# The New Way

```{r}
library(stars)


lake_stars <- st_bbox(lake) %>%
  st_as_stars(dx = 100) %>%
  st_crop(lake)
  
interp = idw(Zn_mg_kg~1, y.sp, lake_stars)



mapview(interp,na.col=NA,col.regions=mapviewGetOption('vector.palette')) + 
  mapview(y.sp, zcol = 'Zn_mg_kg')
```

## Variogram

```{r}

v_zn <- variogram(Zn_mg_kg ~ 1, y.sp)

#v.m = fit.variogram(v, vgm(1, "Exp", 50000, 1))
v.m = fit.variogram(v_zn, vgm(1, 'Mat', 50,1))


```

>>>>>>> 9ab4dcdda34922320d5f127d22e636a2d36b4afe
